Title Goes Here

### 2020-04-16 analysis/paper/paper.Rmd
add a boxplot
working on CV plots

@@

CV_ML <- cv(ML, na.rm = FALSE) #na.rm: logical. Should missing values be removed?
CV_BL <- cv(BL, na.rm = FALSE)
CV_TL <- cv(TL, na.rm = FALSE)
CV_SL <- cv(SL, na.rm = FALSE)
CV_MW <- cv(MW, na.rm = FALSE)
CV_TW <- cv(TW, na.rm = FALSE)
CV_SW <- cv(SW, na.rm = FALSE)

sd(DF$ML)/mean(DF$ML)*100
sd(BL)/mean(BL)*100
sd(TL)/mean(TL)*100
sd(SL)/mean(SL)*100
sd(MW)/mean(MW)*100
sd(TW)/mean(TW)*100
sd(SW)/mean(SW)*100

@@

cv_by_site_df_unnest <-   
cv_by_site_df %>% 
  unnest(cv_by_site)
```

@@

>>>>

Box plot for each attributes
```{r}
boxplot(DF, main = "Variaiton for each attributes", col = "gold")
```

@@

@@

cv_by_site_df_unnest <-   
cv_by_site_df %>% 
  unnest(cv_by_site)

@@

making box plot by phase
```{r]}
cv_boxplot <- cv_by_stage_df_unnest %>% 
  select(-data)
